### 2021-05-10 content/31.tooling-table.tex
citation for SCHeMa
for some reason there are two maDMP mappings

        \textbf{SCHeMa} & Workflow users & PHP & Alpha \\
        \multicolumn{4}{l}{\it Workflow execution using RO-Crate as exchange mechanism } \\

@@

        \textbf{Ro-Crate\_2\_ma-DMP} \citep{doi:10.5281/zenodo.3903463} & Data Management Plan users & Python & Beta \\
        \multicolumn{4}{l}{\it Convert between machine-actionable data management plans (maDMP) and RO-Crate \citep{doi:10.4126/frl01-006423291} }

>>>>

        \textbf{SCHeMa} \citep{athenarc-schema} & Workflow users & PHP & Alpha \\
        \multicolumn{4}{l}{\it Workflow execution using RO-Crate as exchange mechanism \citep{doi:10.5281/zenodo.4671709} } \\

@@

		\textbf{RDA maDMP Mapper} [@doi:10.5281/zenodo.3922136] & Data Management Plan users & Python & Beta \\
		\multicolumn{4}{l}{\it Mapping between machine-actionable data management plans (maDMP) and RO-Crate\citep{doi:10.4126/frl01-006423291} }

        \textbf{Ro-Crate\_2\_ma-DMP} \citep{doi:10.5281/zenodo.3903463} & Data Management Plan users & Python & Beta \\
        \multicolumn{4}{l}{\it Convert between machine-actionable data management plans (maDMP) and RO-Crate }
